---
output: github_document
---

# usahex


## Installation 

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mareichler/usahex")
```

## Hex Maps 

<!--                      |50 states| DC | PR | VI | GU | AS | MP | PW |  --> 
| map name / geos include |50 states| District of Columbia | Puerto Rico | U.S. Virgin Islands | Guam | American Samoa | Northern Mariana Islands | Palau | 
|:-----                   |:----:   |:--:|:--:|:--:|:--:|:--:|:--:|:--:|
| usa50                  | X       | -  | -  | -  | -  | -  | -  | -  |
| usa51                  | X       | X  | -  | -  | -  | -  | -  | -  |
| usa52                  | X       | X  | X  | -  | -  | -  | -  | -  |
| usa53                  | X       | X  | X  | X  | -  | -  | -  | -  |
| usa56                  | X       | X  | X  | X  | X  | X  | X  | -  |
| usaETA                 | X       | X  | X  | X  | X  | X  | X  | X  |
| ETAregions\*           | x       | x  | x  | x  | x  | x  | x  | x  |

\* *Note:* Does not include individual geography hexagons, combines hexagons to create grouped regions of hexagons.  

The original source of the coordinates are from the NPR Graphics team: [github.com/nprapps/dailygraphics-templates](https://github.com/nprapps/dailygraphics-templates/blob/129967a4ae36f14cf299f434f9814f7314a00cde/state_grid_map/index.html#L50-L110). The y values have been reversed so that the plot is not upside down. 


```{r, message = FALSE, warning = FALSE}
library(usahex)
library(tidyverse)
```


```{r}
get_coordinates(map = "usaETA", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(aes(fill = geo_type)) + 
  geom_sf_text(aes(label = abbr_usps)) + 
  theme_void()
```

```{r, eval= FALSE, echo = FALSE}
# above image is not shown in pkgdown website 
# https://github.com/r-lib/pkgdown/issues/133
# https://stackoverflow.com/questions/76778527/home-page-generated-by-pkgdown-not-rendering-properly
```


## Don't Use R? 

Have no fear! I saved a csv of each map with the coordinates.  These files can be found in the data-raw folder on github.   
