---
output: github_document
---

# usahex

US Hex Map with just States: [r-graph-gallery.com/hexbin-map](https://www.r-graph-gallery.com/hexbin-map)


I've copied the coordinates from the NPR Graphics team: [github.com/nprapps/dailygraphics-templates](https://github.com/nprapps/dailygraphics-templates/blob/master/state_grid_map/index.html). The y values have been reversed so that the plot is not upside down.  


# Available Maps


```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(usahex)
```


## `states50`

50 US states only


```{r map-states50}
get_coordinates(map = "states50", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(fill = "grey35", color = "white") + 
  geom_sf_text(aes(label = abbr_usps), color = "white") + 
  theme_void()
```

## `statesDC` 

50 US States and District of Columbia.  

```{r map-statesDC}
get_coordinates(map = "statesDC", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(fill = "grey35", color = "white") + 
  geom_sf_text(aes(label = abbr_usps), color = "white") + 
  theme_void()
```

## `statesTerr` 

50 US States, District of Columbia, and 5 territories: Puerto Rico, Virgin Islands, American Samoa, and the Northern Marina Islands. 

```{r map-statesTerr}
get_coordinates(map = "statesTerr", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(fill = "grey35", color = "white") + 
  geom_sf_text(aes(label = abbr_usps), color = "white") + 
  theme_void()
```

## `WIOAETA` and `WIOAETAregions` 

50 US States, District of Columbia (DC), 5 territories (Puerto Rico, Virgin Islands, American Samoa, and the Northern Marina Islands), and the freely associated state of Palau. 

WIOA: Workforce Innovation and Opportunity (workforce dev. legislation)  
ETA: Department of Labor's Employment and Training Administration

The [ETA regions](https://www.dol.gov/agencies/eta/regions) will rarely be plotted on their own, but they are nice to add as a border to group states in the same region together.   


```{r map-WIOAETA}
get_coordinates(map = "WIOAETA", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(aes(fill = eta_region_name), color = "white") + 
  geom_sf(data = get_coordinates("WIOAETAregions", "hexmap"), 
          fill = NA, color = "grey35", linewidth = 1) + 
  geom_sf_text(aes(label = abbr_usps), color = "white") + 
  theme_void()
```
