---
title: "Available Maps"
date: "2025-07-18"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{Available Maps}
    %\VignetteEncoding{UTF-8}
    %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(usahex)
```


## `states50`

50 US states only


```{r, fig.width = 6.72, fig.height= 4.80, dpi = 96}
get_coordinates(map = "states50", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(fill = "grey35", color = "white") + 
  geom_sf_text(aes(label = abbr_usps), color = "white") + 
  theme_void()
```

## `statesDC` 

50 US States and District of Columbia.  

```{r, fig.width = 6.72, fig.height= 4.80, dpi = 96}
get_coordinates(map = "statesDC", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(fill = "grey35", color = "white") + 
  geom_sf_text(aes(label = abbr_usps), color = "white") + 
  theme_void()
```

## `statesTerr` 

50 US States, District of Columbia, and 5 territories: Puerto Rico, Virgin Islands, American Samoa, and the Northern Marina Islands. 

```{r, fig.width = 6.72, fig.height= 4.80, dpi = 96}
get_coordinates(map = "statesTerr", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(fill = "grey35", color = "white") + 
  geom_sf_text(aes(label = abbr_usps), color = "white") + 
  theme_void()
```

## `WIOAETA` and `WIOAETAregions` 

50 US States, District of Columbia (DC), 5 territories (Puerto Rico, Virgin Islands, American Samoa, and the Northern Marina Islands), and the freely associated state of Palau. 

WIOA: Workforce Innovation and Opportunity (workforce dev. legislation)  
ETA: Department of Labor's Employment and Training Administration

The [ETA regions](https://www.dol.gov/agencies/eta/regions) will rarely be plotted on their own, but they are nice to add as a border to group states in the same region together.   


```{r, fig.width = 6.72, fig.height= 4.80, dpi = 96}
get_coordinates(map = "WIOAETA", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(aes(fill = eta_region_name), color = "white") + 
  geom_sf(data = get_coordinates("WIOAETAregions", "hexmap"), 
          fill = NA, color = "grey35", linewidth = 1) + 
  geom_sf_text(aes(label = abbr_usps), color = "white") + 
  theme_void()
```
