---
title: "Available Maps"
date: "2025-07-18"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{Available Maps}
    %\VignetteEncoding{UTF-8}
    %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

| geos / map name              |`usa50`|`usa51`|`usa52`|`usa53`|`usa56`|`usa59`|`usaETA`/`ETAregions`| 
|:------------                 |:-----:|:-----:|:-----:|:-----:|:-----:|:-----:|:-----:|
| 50 states                    | X     | X     | X     | X     | X     | X     | X     |
| District of Columbia         | -     | X     | X     | X     | X     | X     | X     |
| Puerto Rico - *territory*     | -    | -     | X     | X     | X     | X     | X     |
| U.S. Virgin Islands - *territory*  |-| -     | -     | X     | X     | X     | X     |
| GU, AS, MP - *territories*         |-| -     | -     | -     | X     | X     | X     |
| Palau - *freely associate state*   |-| -     | -     | -     | -     | X     | X     |
| FM & MH - *freely associate states*|-| -     | -     | -     | -     | X     | -     |

```{r, message = FALSE, warning = FALSE}
library(tidyverse)
library(usahex)
```


## `usa50`

50 US states only


```{r, fig.width = 6.72, fig.height= 4.80, dpi = 96}
get_coordinates(map = "usa50", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(fill = "grey35", color = "white") + 
  geom_sf_text(aes(label = abbr_usps), color = "white") + 
  theme_void()
```

## `usa51` 

50 US States and District of Columbia.  

```{r, fig.width = 6.72, fig.height= 4.80, dpi = 96}
get_coordinates(map = "usa51", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(fill = "grey35", color = "white") + 
  geom_sf_text(aes(label = abbr_usps), color = "white") + 
  theme_void()
```

## `usa52` 

50 US States, District of Columbia and Puerto Rico   

```{r, fig.width = 6.72, fig.height= 4.80, dpi = 96}
get_coordinates(map = "usa52", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(fill = "grey35", color = "white") + 
  geom_sf_text(aes(label = abbr_usps), color = "white") + 
  theme_void()
```

## `usa53` 

50 US States, District of Columbia, Puerto Rico and US Virgin Islands   

```{r, fig.width = 6.72, fig.height= 4.80, dpi = 96}
get_coordinates(map = "usa53", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(fill = "grey35", color = "white") + 
  geom_sf_text(aes(label = abbr_usps), color = "white") + 
  theme_void()
```

## `usa56` 

50 US States, District of Columbia, and 5 territories: Puerto Rico, Virgin Islands, American Samoa, and the Northern Marina Islands. 

```{r, fig.width = 6.72, fig.height= 4.80, dpi = 96}
get_coordinates(map = "usa56", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(fill = "grey35", color = "white") + 
  geom_sf_text(aes(label = abbr_usps), color = "white") + 
  theme_void()
```

## `usa59` 

50 US States, District of Columbia, territories (Puerto Rico, Virgin Islands, American Samoa, and the Northern Marina Islands) and freely associated states (Micronesia, Marshall Islands and Palau). 

```{r, fig.width = 6.72, fig.height= 4.80, dpi = 96}
get_coordinates(map = "usa59", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(fill = "grey35", color = "white") + 
  geom_sf_text(aes(label = abbr_usps), color = "white") + 
  theme_void()
```


## `usaETA` and `ETAregions` 

50 US States, District of Columbia (DC), 5 territories (Puerto Rico, Virgin Islands, American Samoa, and the Northern Marina Islands), and the freely associated state of Palau. 

WIOA: Workforce Innovation and Opportunity (workforce dev. legislation)  
ETA: Department of Labor's Employment and Training Administration

The [ETA regions](https://www.dol.gov/agencies/eta/regions) will rarely be plotted on their own, but they are nice to add as a border to group states in the same region together.   


```{r, fig.width = 6.72, fig.height= 4.80, dpi = 96}
get_coordinates(map = "usaETA", coords = "hexmap") |> 
  ggplot() + 
  geom_sf(aes(fill = eta_region_name), color = "white") + 
  geom_sf(data = get_coordinates("ETAregions", "hexmap"), 
          fill = NA, color = "grey35", linewidth = 1) + 
  geom_sf_text(aes(label = abbr_usps), color = "white") + 
  theme_void()
```
