---
title: "CSR for Map"
date: "2025-07-18"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{CSR for Map}
    %\VignetteEncoding{UTF-8}
    %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The **usahex** maps do not need a coordinate reference system (CRS) because they are not based on actual latitude/longitude coordinates.  


This is different from the hex map available from [R Graph Gallery](https://r-graph-gallery.com/hexbin-map); Data for this hex map can be downloaded as a geojson file [here](https://team.carto.com/u/andrew/tables/andrew.us_states_hexgrid/public/map).  Since this is a geojson file; a CRS is required in order to square the a hexagons.  

The differences are illustrated below.  


```{r setup, warning = FALSE, message = FALSE}
library(usahex) 
library(sf)
library(tidyverse)
require(cowplot) 
```


```{r import-data}
sf_usahex <- usahex::usa51
sf_geojson <- read_sf("us_states_hexgrid.geojson") |> 
  # rename abbreviation to match usahex variable name
  rename(abbr_usps = iso3166_2) |> 
  # join to add other abbreviations and fips 
  full_join(st_drop_geometry(sf_usahex), by = "abbr_usps")
```


```{r, out.width = "100%", fig.width = 15, fig.height = 4.5}
gg1 <- ggplot(sf_geojson) + 
  geom_sf() +
  labs(title = "geojson - hexagons vary in size") + 
  theme_void()

gg2 <- ggplot(sf_usahex) + 
  geom_sf() + 
  labs(title = "usahex - all hexagons are the same size") + 
  theme_void()

plot_grid(gg1, gg2)
```

The map with hexagon's based on actual lat/long coordinates results in the hexagons looking slightly 'warped' when plotted in ggplot; the hexagons at the top of the map look smaller than the hexagons at the bottom of the map.  **usahex** hex map is not based on lat/long coordinates.  All hexagons are the same size when plotted.  

In order to 'square' the hexagons based on lat/long coordinates, you need to [update the CRS](#update-crs-to-square-hexagons). 

**Again,  usahex coordinates are not based on lat/long, a CRS is not required for plotting.** 


## Update CRS to Square Hexagons  

It's possible to 'square' the other hex map by changing the coordinate reference system (CRS) to the WGS 84 / Pseudo-Mercator CRS ([EPSG code 3857](https://epsg.org/crs_3857/WGS-84-Pseudo-Mercator.html?sessionkey=330b562ysa)).  


```{r}
sf_geojson <- st_transform(sf_geojson, 3857)
```

```{r, out.width = "100%", fig.width = 15, fig.height = 4.5}
gg1 <- ggplot(sf_geojson) + 
  geom_sf() +
  geom_sf_text(aes(label=abbr_usps)) +
  labs(title = "geojson - hexagons look the same size when change CRS to 3857") + 
  theme_void()

gg2 <- ggplot(sf_usahex) + 
  geom_sf() + 
  geom_sf_text(aes(label=abbr_usps)) +
  labs(title = "usahex - all hexagons are the same size without CRS") + 
  theme_void()

plot_grid(gg1, gg2, nrow = 1)
```


## Two Labels for Each State 

In order to plot two different labels, you will need to have two different points.  Both the geojson hex map and the **usahex** map will need to be transformed.  The geojson needs large numbers in order to adjust the plot location (+/- 100000) becuase the coordinates are actual lat/long values.  The **usahex** maps only needs a small +/- 5 units to adjust the labels.  

```{r, out.width = "100%", fig.width = 15, fig.height = 4.5}
gg1 <-ggplot(sf_geojson) + 
  geom_sf() +
  geom_sf_text(
    data = mutate(sf_geojson, geometry = geometry + c(0, 100000)) |> 
      sf::st_set_crs(3857),  
    aes(label=abbr_usps), 
    fontface = "bold", 
    size = 3.25
  ) +
  geom_sf_text(
    data = mutate(sf_geojson, geometry = geometry + c(0, -100000)) |> 
      sf::st_set_crs(3857),  
    aes(label=fips), 
    size = 2.25
  ) +
  labs(title = "geojson -large adjustment values") + 
  theme_void()

gg2 <- ggplot(sf_usahex) + 
  geom_sf() + 
    geom_sf_text(
    data = mutate(sf_usahex, geometry = geometry + c(0, 5)),  
    aes(label=abbr_usps), 
    fontface = "bold", 
    size = 3.25
  ) +
  geom_sf_text(
    data = mutate(sf_usahex, geometry = geometry + c(0, -5)),  
    aes(label=fips), 
    size = 2.25
  ) +
  labs(title = "usahex - small adjustment values") + 
  theme_void()

plot_grid(gg1, gg2, nrow = 1)
```

