---
title: "Geography Abbreviations and Information"
date: "2025-07-18"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{Geography Abbreviations and Information}
    %\VignetteEncoding{UTF-8}
    %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```



## Abbreviations 

### abbr_usps

2-letter code used by the United States Postal Service (USPS). USPS abbreviations are pulled from Wikipedia's [List of U.S. state and territory abbreviations](https://en.wikipedia.org/wiki/List_of_U.S._state_and_territory_abbreviations). 

### abbr_gpo

Abbreviations from US Government Printing Office (GPO). GPO abbreviations are pulled from Wikipedia's [List of U.S. state and territory abbreviations](https://en.wikipedia.org/wiki/List_of_U.S._state_and_territory_abbreviations). 

*Freely associated states (Micronesia, Marshall Islands, and Palau) do not have GPO abbreviations* 

### abbr_ap 

Abbreviations from the AP Stylebook.  AP abbreviations are pulled from Wikipedia's [List of U.S. state and territory abbreviations](https://en.wikipedia.org/wiki/List_of_U.S._state_and_territory_abbreviations).  


*Territories (Guam, Northern Mariana Islands, Puerto Rico, and U.S. Virgin Islands) and freely associated states (Micronesia, Marshall Islands, and Palau) do not have AP abbreviations* 


### abbr_short 

Abbreviation or name for each geography that is either 3-4 characters. 

### abbr_long

Abbreviation or name for each geography that is 5-6 characters, except for: 

- 4 geographies whose name is less than 5 characters; use full names (Iowa, Ohio, Utah, Guam)
- 3 geographies who long abbreviation is 7-8 characters: 
  * Northern Mariana Islands = N.Mar.I.
  * Marshall Islands = Mar.Is.
  * U.S. Virgin Islands = U.S.V.I. 


## Other Informaiton 

### name 

Name of geographic area.  Names are pulled from Wikipedia's [List of U.S. state and territory abbreviations](https://en.wikipedia.org/wiki/List_of_U.S._state_and_territory_abbreviations). 

### fips

2-digit FIPS code (Federal Information Processing Standard). FIPS codes are pulled from Wikipedia's [List of U.S. state and territory abbreviations](https://en.wikipedia.org/wiki/List_of_U.S._state_and_territory_abbreviations). 

### geo_type 

Type of region: state, federal district, territory, freely associated state


## Data Table of Geography Information 

```{r, echo = FALSE}
DT::datatable(
  sf::st_drop_geometry(usahex::usa59), 
  rownames = FALSE, 
  options=list(
    initComplete = DT::JS(
    # makes headers smaller 
        "function(settings, json) {",
        "$(this.api().table().header()).css({'font-size': '80%'});",
        "}"
    ),
    ordering = FALSE
  )
  ) |> 
  # makes columns smaller 
  DT::formatStyle(columns = c(1:9), fontSize = '80%')
```

