---
title: "Multiple Labels on Hex Map"
output: rmarkdown::html_vignette
vignette: >
    %\VignetteIndexEntry{Multiple Labels on Hex Map}
    %\VignetteEncoding{UTF-8}
    %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


There may be instances where you want to include the geography label as well as another label (such as a value) on the hex map.  


```{r setup, warning=FALSE, message = FALSE}
library(usahex) 
library(sf)
library(tidyverse)
```



Population Change for the US from 2010 to 2020, pulled from Wikipedia using [this code](https://github.com/MarEichler/usahex/blob/main/data-raw/pop_change_data.R)

```{r prep-other-data}
other_data <- read.csv("https://raw.githubusercontent.com/MarEichler/usahex/refs/heads/main/data-raw/us_population_change_2010_to_2020.csv")

title <- "Population Change, 2010 to 2020"

source <- paste0(
      "Source (as of ", 
      format.Date(as.Date("2025-07-28"), '%B %e, %Y'),
      "):\n", 
      "en.wikipedia.org/wiki/List_of_states_and_territories_of_the_United_States_by_population"
)
```


Pull the hexagon coordinates  using `get_coordinates()` function.  

```{r pull-hex-coords}
hexmap <- get_coordinates("usaETA", "hexmap")
```


Join the coordinates data with the the population change data. 

```{r combine-data}
combined <- left_join(hexmap, other_data, by = "name")
```

Plot data with state label and value label of percentage change in population.  

```{r create-chart, fig.width=7.15, fig.height=5.2, warning = FALSE}

NA_color <- "grey80"
# RColorBrewer::brewer.pal(3, "PiYG")
scale_colors <- c("#E9A3C9", "#F7F7F7", "#A1D76A") 

ggplot(combined) + 
  geom_sf(aes(fill = perc),     color = NA       ) +  #color (non-NA) hex
  geom_sf(    fill = NA,          aes(color = "NA")    ) +  #dummy for NA values 
  geom_sf(    fill = NA,              color = "grey50" ) +  #hex borders 
  geom_sf_text(
    data=mutate(combined, geometry=geometry+c(0, 5)) # adj state label up by 5
    , aes(label=abbr_usps)
    , fontface="bold"
    , size=3.25
  ) + 
  geom_sf_text(
    data=mutate(combined, geometry=geometry+c(0,-5)) # adj percent label down by 5
    , aes(label=perc_label)
    , size=2.5
  ) + 
  scale_fill_gradient2(
    name = "Percent\nChange"
    , low  = scale_colors[1]
    , mid  = scale_colors[2]
    , high = scale_colors[3]
    , midpoint = 0
    , labels = ~sprintf("%1.f%%", .x)
    , na.value = NA_color
  ) + 
  scale_color_manual( #dummy legend for NA color 
      name = NULL
    , values = NA_color
    , labels = 'No data'
  ) +
  guides(
      fill  = guide_colorbar(order = 1)
    , color = guide_legend(override.aes = list(fill =NA_color))
  ) +
  labs(
    title = title, 
    caption = source
  ) +
  theme_void()
```





